Reproducibility of SNP calling in multiple sequencing runs from single tumors

### 2014-07-03 PAPER/rough_draft.tex
finished the box plots for the filter analysis and added them to the paper draft

>>>>

\begin{figure}
\includegraphics[scale=1.0]{boxplot_number_filtered.png}
\caption{Boxplot of the total number of putative SNPs removed by each of six filters, in each of 379 sequencing samples, from 311 patients. The x-axis gives the name of those filters that removed putative SNPs, and the y-axis gives, on a log scale, the number of mutations removed by a given sample.}
\end{figure}

\begin{figure}
\includegraphics[scale=1.0]{boxplot_percent_overlap_filtered.png}
\caption{Boxplot of the percentage of putative SNPs making up the overlap between the WGS and WGA sequences of a single sample that was removed by a given filter. The x-axis describes the filters, and the y-axis gives the percentage of the overlap removed.}
\end{figure}
